The Name of the Title Is Hope

### 2024-11-09 paper/paper.tex
Added some diff priv

@@

@@

@@

% \begin{figure}[h]
%   \centering
%   \includegraphics[width=\linewidth]{sample-franklin}
%   \caption{1907 Franklin Model D roadster. Photograph by Harris \&
%     Ewing, Inc. [Public domain], via Wikimedia
%     Commons. (\url{https://goo.gl/VLCRBB}).}
%   \Description{A woman and a girl in white dresses sit in an open car.}
% \end{figure}

>>>>

\usepackage{mathtools}

\graphicspath{{images/}}
\DeclareGraphicsExtensions{.pdf}

\DeclarePairedDelimiter{\set}{\{}{\}}
\DeclarePairedDelimiter{\tuple}{(}{)}
\DeclarePairedDelimiter{\abs}{\lvert}{\rvert}
\renewcommand{\implies}{\rightarrow}
\newcommand{\db}{\mathcal{D}}
\newcommand{\model}{\mathcal{M}}
\newcommand{\priv}{R}
\newcommand{\pos}{\hat{P}}
\newcommand{\posm}{\hat{P}_\mathcal{M}}
\newcommand{\tru}{T}
\newcommand{\leg}{L}
\newcommand{\sco}{\hat{S}}
\newcommand{\scom}{\hat{S}_\mathcal{M}}
\newcommand{\calib}{C}
\newcommand{\prob}[1]{\text{Pr}[#1]}

@@

A \emph{row} $r_i$ is a lookup table or dictionary. A \emph{database} $\db = \set{r_1, r_2, ...}$ is a collection of rows. The attributes of $\db$ is $\mathcal{A} = \set{A_1, A_2, ...}$. The domain of $A_i$ is $\Omega_i$.

Let $C \subseteq \mathcal{A}$. Let $\Omega_C = \Pi_{i \in C} \Omega_i$. The \emph{marginal}\cite{barak2007privacy,mckenna2021winning} on $C$ is a vector $\mu \in \mathbb{R}^{\abs{\Omega_C}}$, indexed by domain element $t \in \Omega_C$, such that each entry is a count $\mu_t = \Sigma_{x \in \db} \vmathbb{1} [x_C = t]$ where $\vmathbb{1}$ is the indicator function. Let $M_C(\db)$ be the function that computes the marginal on $C$, i.e., $\mu = M_C(\db)$.

A \emph{randomized mechanism} is a randomized algorithm $M$ that takes a database $\db$ and, after, introducing noise, outputs some results in set $R$.

The $p$-norm is denoted by $L_p$ and the $p$-norm of a vector $x$ is denoted by $\Vert x \Vert_p$.

The normal distribution or Gaussian distribution with mean $\mu$ and standard deviation $\sigma$ is denoted by $\mathcal{N}(\mu, \sigma^2)$.

The Kullback–Leibler divergence between probability distributions $P$ and $Q$ is denoted by $D_{KL}(P \Vert Q)$. The generalization of it, R\'enyi divergence\cite{van2014renyi}, of order $\alpha$ is denoted by $D_\alpha(P \Vert Q)$.

@@

\begin{definition}[Sensitivity\cite{dwork2014algorithmic}]\label{def:sensitivity}
Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The $L_2$ sensitivity of $f$ is for all databases $\db_1,\db_2$ that differ in exactly one row:
\[
\Delta^2_f = max_{\db_1,\db_2} \Vert f(\db_1) - f(\db_2) \Vert_p
\]
\end{definition}

\begin{definition}[Gaussian Mechanism\cite{dwork2014algorithmic}]\label{def:gm}
Let $f$ be a function that takes a database $\db$ and outputs a vector $\mathbb{R}^p$. The Gaussian Mechanism $M$ adds Gaussian noise with scale $\sigma$ to each of the $p$ outputs:
\[
M(\db) = f(\db) + \mathcal{N}(0, \sigma^2 \mathbb{I})
\]
\end{definition}

\begin{definition}[Differential Privacy (DP) \cite{dwork2006calibrating,dwork2014algorithmic,mckenna2021winning}]\label{def:rdp}
A randomized mechanism $M$ satisfies $(\epsilon,\delta)$-DP if, for all databases $\db_1,\db_2$ that differ in exactly one row and for all subsets $S$ of $R$, we have
\[
\prob{M(\db_1) \in S} \leq e^\epsilon \prob{M(\db_2) \in S} + \delta
\]
\end{definition}

\begin{definition}[R\'enyi Differential Privacy (RDP)]\label{def:rdp}
A randomized mechanism $M$ satisfies $(\alpha,\gamma)$-RDP for $\alpha \geq 1$ and $\gamma \geq 1$ if, for all databases $\db_1,\db_2$ that differ in exactly one row, we have
\[
D_\alpha(M(\db_1) \Vert M(\db_2)) \leq \gamma
\]
\end{definition}

\begin{theorem}[RDP of the Gaussian Mechanism\cite{feldman2018privacy,mironov2017renyi}]
The Gaussian Mechanism satisfies $(\alpha, \alpha \frac{\Delta^2_f}{2 \sigma^2})$-RDP.
\end{theorem}

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{compas_mst}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{adult_mst}
  \caption{1907 Franklin Model D roadster. Photograph by Harris \&
    Ewing, Inc. [Public domain], via Wikimedia
    Commons. (\url{https://goo.gl/VLCRBB}).}
  \Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}
